Leadership across cultures and contexts: an exploratory analysis

### 2020-04-29 leadership_across_cultures_contexts.Rmd

Our qualities and functions data comprised sparse $`r nrow(all_data)` \times `r length(quality_vars)`$ and $`r nrow(all_data)` \times `r length(function_vars)`$ matrices of binary data, respectively. Most data reduction methods did not find strong evidence of structure in the data. We therefore explored reduced matrices that removed uninformative rows with no evidence for any variable and columns with only a few text records with evidence. Stable clusters emerged with $`r nrow(df_qual)` \times `r ncol(df_qual)`$ and $`r nrow(df_func)` \times `r ncol(df_func)`$ matrices for qualities and functions, respectively.

>>>>

Our qualities and functions data comprised sparse $`r nrow(all_data)` \times `r length(quality_vars)`$ and $`r nrow(all_data)` \times `r length(function_vars)`$ matrices of binary data, respectively. Most data reduction methods did not find strong or stable evidence of structure in the data. We therefore explored reduced matrices that removed uninformative rows with no evidence for any variable, and variables with only a few rows with evidence. Stable clusters emerged with $`r nrow(df_qual)` \times `r ncol(df_qual)`$ and $`r nrow(df_func)` \times `r ncol(df_func)`$ matrices for qualities and functions, respectively.
